\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{tabularx}
\usepackage{fontawesome5}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.6in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-0.6in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Jenil Kukadiya} \\ \vspace{1pt}
    Ahmedabad, India \\ \vspace{1pt}
    \small \raisebox{-0.1\height}{\faPhone} 9909072743 ~ 
    \href{mailto:jenilkukadiya82@gmail.com}{\raisebox{-0.2\height}{\faEnvelope} \underline{jenilkukadiya82@gmail.com}} ~ 
    \href{https://linkedin.com/in/jenil-kukadiya-341925210/}{\raisebox{-0.2\height}{\faLinkedin} \underline{linkedin.com/in/jenil-kukadiya-341925210}} ~
    \href{https://github.com/jenil_kukadiya}{\raisebox{-0.2\height}{\faGithub} \underline{github.com/jenil\_kukadiya}}
    \vspace{-8pt}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Nirma University}{Ahmedabad, Gujarat}
      {B.Tech in Computer Science Engineering}
  \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}: C++, Java, C, SQL, PostgreSQL, Python, HTML/CSS \\
     \textbf{Frameworks/Libraries}: Spring Boot, Spring MVC, Node.js \\
     \textbf{Developer Tools}: Git, GitHub, VS Code, IntelliJ, Eclipse \\
     \textbf{Core Concepts}: Data Structures and Algorithms, Competitive Coding, Database Management Systems, Operating Systems, Object-Oriented Programming \\
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeItemListStart

    \resumeSubheading
  {Freelance Full Stack Developer}{Feb. 2021 -- Present}
  {Remote}{}
  \resumeItemListStart
    \resumeItem{Developed and maintained enterprise-grade applications using \textbf{Spring Boot} and \textbf{React.js}, following clean architecture and microservice principles.}
    \resumeItem{Built and integrated \textbf{RESTful APIs} across distributed services with secure authentication, logging, and role-based access control.}
    \resumeItem{Containerized microservices using \textbf{Docker} and managed CI/CD pipelines via \textbf{Azure DevOps} for automated deployments to QA and production.}
    \resumeItem{Implemented multi-environment configurations using \textbf{Spring Profiles} and externalized property management for flexible deployments.}
    \resumeItem{Collaborated with clients to gather requirements, estimate scope, and deliver fully tested features using agile methodologies and version control practices.}
    \resumeItem{Utilized Azure services such as \textbf{App Services}, \textbf{Blob Storage}, and \textbf{Key Vault} to enhance scalability, security, and observability.}
  \resumeItemListEnd

  
    \resumeSubheading
      {SDE 1}{Jul. 2024 -- Present}
      {Ajmera Infotech}{Ahmedabad, India}
      \resumeItemListStart
        \resumeItem{Developed a microservice for email journey management using \textbf{Node.js} and \textbf{Zoho CRM APIs}.}
        \resumeItem{Built RESTful APIs, optimized database performance, and worked on microservices architecture.}
        \resumeItem{Integrated third-party services for scalability and enhanced system functionality.}
        \resumeItem{Designed and implemented a \textbf{Team Management System} to automate HR operations using \textbf{Bubble.io}, \textbf{AWS Lambda}, and \textbf{API Gateway}.}
        \resumeItem{Fetched worked hours from \textbf{Zoho People Plus} and validated them against policy rules (e.g., full-day, half-day, weekends). Triggered alert emails if minimum criteria were not met.}
        \resumeItem{Integrated \textbf{Jira} to extract client-specific employee worklogs for accurate billing.}
        \resumeItem{Developed multiple admin dashboards (Departments, Skills, Roles, Batches, etc.) as per manager requirements with role-based access.}
      \resumeItemListEnd
    \vspace{-1em} % Adjust this value if needed
    \resumeSubheading
      {SDE Intern}{Jan. 2024 -- Jun. 2024}
      {Ajmera Infotech}{Ahmedabad, India}
      \resumeItemListStart
        \resumeItem{Enhanced RedPen with Spring Boot and PostgreSQL, collaborating with cross-functional teams to resolve bugs, optimize database queries, and improve the admin panel’s usability, ensuring a seamless user experience.}
        \resumeItem{Gained practical experience with AWS services, expanding understanding of cloud infrastructure applications.}
        \resumeItem{Utilized AWS services (SQS, SNS, Cognito) to enhance microservice functionality, modifying backend code for seamless integration with AWS services.}
      \resumeItemListEnd
  \resumeItemListEnd


%-----------PROJECTS-----------
\section{Projects}
\resumeItemListStart

  \resumeProjectHeading
  {\textbf{SecureShots – Secure Gallery Sharing Platform} \hfill \emph{Spring Boot, React, Cloudinary, PostgreSQL, Docker}}{2023}
\resumeItemListStart
  \resumeItem{Built a password-protected gallery app allowing users to create and share photo albums with fine-grained access control.}
  \resumeItem{Integrated Cloudinary to store photos using signed URLs, preventing unauthorized public access.}
  \resumeItem{Implemented JWT-based login and role-based authorization to control secure user access.}
  \resumeItem{Used PostgreSQL for managing users, galleries, and image metadata in a relational structure.}
  \resumeItem{Developed REST APIs with Spring Boot and a responsive React.js frontend with conditional rendering.}
  \resumeItem{Deployed backend on Render using Docker; configured CORS for secure communication between frontend and backend.}
\resumeItemListEnd


  \resumeProjectHeading
    {\textbf{Hospital Management System (MERN Stack)} \hfill \emph{MongoDB, Express.js, React.js, Node.js, JWT}}{2022}
    \resumeItemListStart
      \resumeItem{Developed a comprehensive hospital management platform to streamline appointment scheduling, patient record management, and admin operations.}
      \resumeItem{Implemented user roles for patients, doctors, and administrators, each with tailored dashboards and permissions.}
      \resumeItem{Utilized JWT authentication and protected routes for secure access to sensitive medical data.}
      \resumeItem{Designed RESTful APIs with Express and Node.js, and stored structured health and appointment data using MongoDB.}
      \resumeItem{Created a responsive React frontend with Redux for global state management and dynamic routing.}
      \resumeItem{Followed best practices for code structuring, security, and user experience throughout the application.}
    \resumeItemListEnd

\resumeItemListEnd




%---------ACHIEVEMENTS-----------------
\section{Achievements}
\resumeItemListStart
    \resumeItem{\textbf{Competitive Programming:}}
    \begin{itemize}
        \item \textbf{Expert} on Codeforces (\href{https://codeforces.com/profile/jenil_kukadiya}{jenilkukadiya}, Max: 1666)
        \item \textbf{Guardian} on Leetcode (\href{https://leetcode.com/u/jenilkukadiya/}{jenilkukadiya}, Max: 2197)
        \item Rank 445 in Leetcode Weekly Contest 358 (27k participants)
        \item Rank 460 in Leetcode Weekly Contest 359 (27k participants)
        \item Rank 472 in Google Kickstart E 2022 (18k participants)
        \item ICPC Kanpur-Mathura 2022 Rank 384
    \end{itemize}
    
\resumeItem{\textbf{Additional Links:}}
    \begin{itemize}
        \item \textbf{CodeChef}: \href{https://www.codechef.com/users/jenil_kukadiya}{jenilkukadiya}
        \item \textbf{LinkedIn}: \href{https://www.linkedin.com/in/jenil-kukadiya-341925210/}{jenilkukadiya}
    \end{itemize}
\resumeItemListEnd

\section{Campus Activities}
  \resumeSubHeadingListStart
  \resumeSubheading
      {CodeAdda Programming Club}{Oct. 2022 -- Nov. 2023}
      {Member}{}
      \resumeItemListStart
        \resumeItem{Organised contests on various websites such as hackerrank,
codeforces, etc to improve coding culture in our university. Took
sessions for juniors as well as peers for teaching data structures
and algorithms.}
   \resumeSubHeadingListEnd


% %-----------LEADERSHIP---------------
% \section{Leadership \& Extracurricular}
%   \resumeItemListStart
%     \resumeSubheading
%         {CODEADDA Programming Club}{Member}{2020 -- Present}
%         \resumeItemListStart
%             \resumeItem{Organized contests on Codeforces to improve coding culture at the university.}
%             \resumeItem{Mentored juniors in programming, taught sessions on data structures and algorithms.}
%         \resumeItemListEnd
%   \resumeItemListEnd

\end{document}
